Molecular transport in human pial perivasculature

### 2024-11-27 paper/supplementary_main.tex
Move some facet notation definitions to where they are needed. Still need to sort out the details for the Stokes flow
Former-commit-id: 61d724ce8109ac4d1afc5a4ef0eed3ea7fcf6a6e [formerly 61d724ce8109ac4d1afc5a4ef0eed3ea7fcf6a6e [formerly 9a035bc844e88182c4f65a712129b9f1871bd6aa]]
Former-commit-id: 8f1e5a788ed7ec5874b9287bcee44aabf43b5fe1
Former-commit-id: 9d49eeb9c59ddc949f4d612bb9fbbf2348985446

\subsubsection{Computational mesh entities: definitions and notation}

We consider a mesh $\mathcal{T} = \{ E \}$ of $\Omega = \Omega_{\rm
  PAR} \cup \Omega_{\rm CSF}$, consisting of tetrahedral mesh cells
$E$, and conforming to the domains $\Omega_{\rm PAR}$ and $\Omega_{\rm
  CSF}$ and to the CSF-brain interface $\Gamma_{\rm pia} \cup
\Gamma_{\rm LV}$. We denote the restriction of $\mathcal{T}$ to
$\Omega_{\rm PAR}$ and $\Omega_{\rm CSF}$ by $\mathcal{T}_{\rm PAR}$
and $\mathcal{T}_{\rm CSF}$, respectively. The collection of all
interior facets (i.e.~triangular faces of the tetrahedral mesh cells)
in $\mathcal{T}_{\rm PAR}$ and $\mathcal{T}_{\rm CSF}$ are denoted by
$\mathcal{F}_{i, \rm PAR}$ and $\mathcal{F}_{i, \rm CSF}$,
respectively. We define the union of facets interior both to
$\mathcal{T}_{i, \rm PAR}$ and $\mathcal{T}_{i, \rm CSF}$ as
$\mathcal{F}_i = \mathcal{F}_{i, \rm PAR} \cup \mathcal{F}_{i, \rm
  CSF}$. Facets lying on the pial interface $\Gamma_{\rm pia}$ are
denoted by $\mathcal{F}_{\rm pia}$, on the outer (arachnoid) boundary
$\Gamma_{\rm AM}$ by $\mathcal{F}_{\rm AM}$, on the inner ventricular
interface $\Gamma_{\rm LV}$ by $\mathcal{F}_{\rm LV}$, on the boundary
toward the spinal cord $\Gamma_{\rm SC}$ by $\mathcal{F}_{\rm SC}$ and
on the boundary towards the spinal SAS $\Gamma_{\rm SSAS}$ by
$\mathcal{F}_{\rm SSAS}$. \discuss{For convenience, we denote
  $\mathcal{F}_e = \mathcal{F}_{\rm pia} \cup \mathcal{F}_{\rm LV}
  \cup \mathcal{F}_{\rm AM-U} \cup \mathcal{F}_{\rm SSAS}$, and the
  union of all facets in $\mathcal{T}$ is denoted by $\mathcal{F} =
  \mathcal{F}_i \cup \mathcal{F}_e \discuss{\cup \mathcal{F}_{\rm SC}
    \cup \mathcal{F}_{\rm AM-L}}$.}

@@

We consider an H(div)-based finite element approximation of the incompressible Stokes equations~\eqref{eq:stokes} defined over $\Omega_{\rm CSF}$ with the boundary conditions~\eqref{eq:stokes_bcs}. Following\cite{hong2016robust}, we approximate the velocity field $\bm u$ and the pressure field $p$ with the following finite element spaces:
\begin{align*}
  \bm V_h &= \{ \bm v  \in H(\mathrm{div}, \Omega_{\mathrm{CSF}}): \;
  \bm v \vert_{E} \in \mathrm{BDM}^2(E), \; E \in \mathcal{T}_{\rm CSF}; \;
  \bm v \cdot \bm n = 0
  \text{ on } \Gamma_{\rm{pia}} \cup \Gamma_{\rm AM-L} \cup \Gamma_{\rm{SSAS}}, \;\; \bm v \cdot \bm n = \frac{1}{|\Gamma_{\mathrm{LV}}|} u_{\mathrm{in}} \text{ on } \Gamma_{\mathrm{LV}} \}  \\ 
  Q_h  &= \{q \in L^2(\Omega_{\rm CSF}): \; q \vert_E \in \mathbb{P}^1(E),
  \; E \in \mathcal{T}_{\rm CSF} \}. 
\end{align*}
Here, $H(\mathrm{div}, \Omega)$ is the space of $L^2(\Omega)$ vector fields with $L^2(\Omega)$ divergence, $\mathrm{BDM}^2$ is the Brezzi-Douglas--Marini element~\cite{brezzi1987mixed} of degree 2, and $\bm n$ and $\bm \tau$ are the unit outward normal and unit tangent vectors to each facet, respectively. Given any vector $\bm v$, the normal and tangential components on each facet are denoted and given by 
\begin{equation}
\bm v_n = (\bm v \cdot \bm n) \bm n, \quad \bm v_t = \bm v - \bm v_n. 
\end{equation}
Since $\bm V_h \subset H(\mathrm{div}, \Omega_{\rm CSF})$, then $[\bm v_n] = 0 $ on $\mathcal{F}_{i, \rm CSF}$. Continuity in the tangential component is enforced weakly via interior penalization. Define the form \mer{MER: Check $\Gamma_{\rm AM}$ part. 26.11.24: Rami will check $\mathcal{F}_e$ versus definitions of the boundaries and where it appears.}
\begin{multline}
  \mathcal{A}_h(\bm u, \bm v)
  = \sum_{E \in \mathcal{T}_{\rm CSF}} \int_{E} \mu \nabla \bm u : \nabla \bm v
  - \sum_{F \in \discuss{\mathcal{F}_{i, \rm CSF} \cup \mathcal{F}_{e}}} \left (
  \int_{F} \mu \{\nabla \bm u\} \cdot \bm n_F \cdot [\bm v_t] 
  - %\sum_{F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma}}
  \int_{F} \mu \{\nabla \bm v\}\cdot \bm n_F \cdot [\bm u_t]
  + %\sum_{F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma}}
  \frac{\sigma \mu}{h} \int_{F} [\bm u_t ] \cdot [\bm v_t] \right ),   
\end{multline}
where \discuss{$h$ denotes the element size}. We set the penalty parameter for the tangential continuity to be $\sigma = 20$. Our finite element discretization of the incompressible Stokes equations is then to find $(\bm u_h, p_h) \in \bm V_h \times Q_h$ such that 
\begin{subequations}
\begin{align}
  \mathcal{A}_h(\bm u_h, \bm v_h)
  + \sum_{F \in \mathcal{F}_{\rm AM-U}} \int_{F} R_0 (\bm u_h \cdot \bm n) (\bm v_h \cdot \bm n)
  - \int_{\Omega_{\rm CSF}} \nabla \cdot \bm v_h \, p_h  &= 0, \qquad \foralls \bm v_h \in \bm V_h, \\ 
\int_{\Omega_{\rm CSF}} \nabla \cdot \bm u_h \, q_h  &= 0, \qquad \foralls q_h \in Q_h.
\end{align}
\end{subequations}

>>>>

\subsubsection{Computational mesh entities: definitions and common notation}

We consider a mesh $\mathcal{T} = \{ E \}$ of $\Omega = \Omega_{\rm
  PAR} \cup \Omega_{\rm CSF}$, consisting of tetrahedral mesh cells
$E$, and conforming to the domains $\Omega_{\rm PAR}$ and $\Omega_{\rm
  CSF}$ and to the CSF-brain interface $\Gamma_{\rm pia} \cup
\Gamma_{\rm LV}$. We denote the restriction of $\mathcal{T}$ to
$\Omega_{\rm PAR}$ and $\Omega_{\rm CSF}$ by $\mathcal{T}_{\rm PAR}$
and $\mathcal{T}_{\rm CSF}$, respectively. The collection of all
interior facets (i.e.~triangular faces of the tetrahedral mesh cells)
in $\mathcal{T}_{\rm PAR}$ and $\mathcal{T}_{\rm CSF}$ are denoted by
$\mathcal{F}_{i, \rm PAR}$ and $\mathcal{F}_{i, \rm CSF}$,
respectively. We define the union of facets interior both to
$\mathcal{T}_{i, \rm PAR}$ and $\mathcal{T}_{i, \rm CSF}$ as
$\mathcal{F}_i = \mathcal{F}_{i, \rm PAR} \cup \mathcal{F}_{i, \rm
  CSF}$.

@@

We consider an H(div)-based finite element approximation of the incompressible Stokes equations~\eqref{eq:stokes} defined over $\Omega_{\rm CSF}$ with the boundary conditions~\eqref{eq:stokes_bcs}. Following\cite{hong2016robust}, we approximate the velocity field $\bm u$ and the pressure field $p$ with the following finite element spaces:
\begin{align*}
  \bm V_h &= \{ \bm v  \in H(\mathrm{div}, \Omega_{\mathrm{CSF}}): \;
  \bm v \vert_{E} \in \mathrm{BDM}^2(E), \; E \in \mathcal{T}_{\rm CSF}; \;
  \bm v \cdot \bm n = 0
  \text{ on } \Gamma_{\rm{pia}} \cup \Gamma_{\rm AM-L} \cup \Gamma_{\rm{SSAS}}, \;\; \bm v \cdot \bm n = \frac{1}{|\Gamma_{\mathrm{LV}}|} u_{\mathrm{in}} \text{ on } \Gamma_{\mathrm{LV}} \}  \\ 
  Q_h  &= \{q \in L^2(\Omega_{\rm CSF}): \; q \vert_E \in \mathbb{P}^1(E),
  \; E \in \mathcal{T}_{\rm CSF} \}. 
\end{align*}
Here, $H(\mathrm{div}, \Omega)$ is the space of $L^2(\Omega)$ vector fields with $L^2(\Omega)$ divergence, $\mathrm{BDM}^2$ is the Brezzi-Douglas--Marini element~\cite{brezzi1987mixed} of degree 2, and $\bm n$ and $\bm \tau$ are the unit outward normal and unit tangent vectors to each facet, respectively. Given any vector $\bm v$, the normal and tangential components on each facet are denoted and given by 
\begin{equation}
\bm v_n = (\bm v \cdot \bm n) \bm n, \quad \bm v_t = \bm v - \bm v_n. 
\end{equation}
Since $\bm V_h \subset H(\mathrm{div}, \Omega_{\rm CSF})$, then $[\bm v_n] = 0 $ on $\mathcal{F}_{i, \rm CSF}$. Continuity in the tangential component is enforced weakly via interior penalization. Facets lying on the pial interface $\Gamma_{\rm pia}$ are
denoted by $\mathcal{F}_{\rm pia}$, on the outer (arachnoid) boundary
$\Gamma_{\rm AM}$ by $\mathcal{F}_{\rm AM}$, on the inner ventricular
interface $\Gamma_{\rm LV}$ by $\mathcal{F}_{\rm LV}$, on the boundary
toward the spinal cord $\Gamma_{\rm SC}$ by $\mathcal{F}_{\rm SC}$ and
on the boundary towards the spinal SAS $\Gamma_{\rm SSAS}$ by
$\mathcal{F}_{\rm SSAS}$.
\discuss{For convenience, we denote
  $\mathcal{F}_e = \mathcal{F}_{\rm pia} \cup \mathcal{F}_{\rm LV}
  \cup \mathcal{F}_{\rm AM-U} \cup \mathcal{F}_{\rm SSAS}$, and the
  union of all facets in $\mathcal{T}$ is denoted by $\mathcal{F} =
  \mathcal{F}_i \cup \mathcal{F}_e \discuss{\cup \mathcal{F}_{\rm SC}
    \cup \mathcal{F}_{\rm AM-L}}$.}
Now, define the form 
\begin{multline}
  \mathcal{A}_h(\bm u, \bm v)
  = \sum_{E \in \mathcal{T}_{\rm CSF}} \int_{E} \mu \nabla \bm u : \nabla \bm v
  - \sum_{F \in \discuss{\mathcal{F}_{i, \rm CSF} \cup \mathcal{F}_{e}}} \left (
  \int_{F} \mu \{\nabla \bm u\} \cdot \bm n_F \cdot [\bm v_t] 
  - %\sum_{F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma}}
  \int_{F} \mu \{\nabla \bm v\}\cdot \bm n_F \cdot [\bm u_t]
  + %\sum_{F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma}}
  \frac{\sigma \mu}{h} \int_{F} [\bm u_t ] \cdot [\bm v_t] \right ),   
\end{multline}
where \discuss{$h$ denotes the element size}. We set the penalty parameter for the tangential continuity to be $\sigma = 20$. Our finite element discretization of the incompressible Stokes equations is then to find $(\bm u_h, p_h) \in \bm V_h \times Q_h$ such that 
\begin{subequations}
\begin{align}
  \mathcal{A}_h(\bm u_h, \bm v_h)
  + \sum_{F \in \discuss{\mathcal{F}_{\rm AM-U}}} \int_{F} R_0 (\bm u_h \cdot \bm n) (\bm v_h \cdot \bm n)
  - \int_{\Omega_{\rm CSF}} \nabla \cdot \bm v_h \, p_h  &= 0, \qquad \foralls \bm v_h \in \bm V_h, \\ 
\int_{\Omega_{\rm CSF}} \nabla \cdot \bm u_h \, q_h  &= 0, \qquad \foralls q_h \in Q_h.
\end{align}
\end{subequations}

\mer{MER: Stopped here.}
